Compact Core Galaxies in the RESOLVE Survey

### 2016-04-18 paperdraft.tex
more new pics
first draft!

\documentclass[iop,apj,twocolappendix]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\title{The Formation and Evolution of Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Mark N. Norris\altaffilmark{3}}
\author{Callie Hood\altaffilmark{1}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Christine Ray\altaffilmark{1,4}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{the RESOLVE Team}
\affil{$^1$University of North Carolina at Chapel Hill}
\affil{$^2$National Optical Astronomical Observatory}
\affil{$^3$University of Central Lancashire}
\affil{$^4$Rutgers, The State University of New Jersey}
\begin{abstract}
We analyze the complete set of compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments. CCGs include both compact ellipticals (cEs) and compact cores surrounded by an envelope of gas and stars, which may represent earlier or later evolutionary stages of cEs. We select CCGs to have core-only radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. CCGs naturally occur in a range of environments from isolated to cluster. With GALEX NUV data, we derive star formation histories and find that a significant number of CCGs have recently formed stars. We compare velocity dispersions of CCGs derived from Gemini IFU data to velocity dispersions of other RESOLVE galaxies derived from SOAR spectroscopy. We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively. Initial results show several CCGs following the dissipative formation track.
\end{abstract}

\keywords{galaxies: formation; galaxies: evolution}
\maketitle

@@

\noindent The term compact stellar system (CSS) composes a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es). Different types of CSSs include ultra compact dwarf galaxies (UCDs; \citet{Phillipps2001}), compact elliptical galaxies (cEs; \citet{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).  There are many unanswered questions about these types of galaxies, typically involving how they form and evolve. One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are in an intermediate and short-lived evolutionary phase, or simply hard to find due to their size. Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.

\subsection{Introduction to UCDs}
UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \citet{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\citet{Drinkwater2000}, \citet{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\citet{Bekki2001}, \citet{Bekki2003}, \citet{Jennings2015}, \citet{Zhang2015}). Meanwhile, \citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546. \citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy.

 \subsection{Introduction to cEs}
cEs, the intermediate-sized CSSs of the three previously mentioned have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}). They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (Choi, Guhathakurta \& Johnson 2002, Graham 2002), or as a part of the low mass extension to the elliptical galaxy population. The evidence for tidal stripping includes finding tidal streams near cEs (Smith Castelli 2008, Chilingarian 2009) and one cE, studied in Kormendy 1997 that is believed to host a central massive black hole. (Threshed spiral scenario: Davidge, Beck \& McGregor 2008). On the other hand, Kormendy \& Bender 2012 argue that cEs can be the extension of normal elliptical galaxies, based on

\subsection{Introduction to dEs and dE,Ns}
dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \citet{Norris2014}). Similarly to cEs, dEs and dE,Ns are though to be tidally stripped remnants (Crnojevic 2014 - dEs in M31 show signs of tidal stripping) or the low mass extension to elliptical galaxies (Steve Crawfords work on high-z LCBDs). They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched. There is some evidence that dE,Ns are the progenitors of UCDs (\citet{Pfeffer2013}, \citet{Zhang2015}, \citet{Liu2015}).

\subsection{Environments of UCDs}
UCDs have been primarily found in clusters, such as Coma (\citet{Price2009}, \citet{Madrid2010}), Fornax (\citet{Hilker1999}, \citet{Drinkwater2000}), Virgo (\citet{Hasegan2005}, \citet{Jones2006}), Centaurus (\citet{Mieske2009}), and Hydra I (\citet{Wehner2007}, \citet{Misgeld2008}). Fewer UCDs have been found in groups: \citet{Evstigneeva2007} find one definite and two candidate UCDs in the Dorado group as well as two candidates in the NGC1400 group. Addititonally, \citet{Hau2009} find a UCD near the Sombrero galaxy.

\subsection{Environments of cEs}
cEs suffer the same issue: they are mainly found in clusters (\citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}) and groups (Chilingarian \& Bergond 2010, \citet{Huxor2011}), but recently more have been found in an isolated environment. \citet{Huxor2013}, \citet{Paudel2014}. There is also recent work by Chilingarian 2015 that finds more isolated

\subsection{Environments of dEs}
dEs have also primarily been found in groups -- Crnojevic et al. 2014 - dEs in M31, Penny 2014) and clusters (\citep{SmithCastelli2012}, Koo 1994, Guzman 1996, Michielson 2008, Steve Crawford's papers).

\subsection{How environments impact formation scenarios}
Thus, there's been no ubiquitous sample of CSSs that allow us to analyze the formation as a function of all environments. These studies mostly focus on selecting targets in the group/cluster environments, since this route is more convenient. Only recently have CSSs been found in the field environment (\citet{Huxor2013}, \citet{Chilingarian2015}), which highlights the need for a statistical census of CSSs that spans the group to cluster to field environments.

\noindent Our goal is to create a complete and volume-limited sample of compact galaxies across all environments so that we may study their evolutionary sequences. For this, we derive our sample from the RESOLVE survey, as described in (\autoref{resolve}). We also use the objects in the Archive of Intermediate Mass Stellar Systems (AIMSS) for comparisons to our sample (\autoref{aimss}). We describe our sample selection process in \autoref{samples} and lastly, describe our spectroscopic data collection and analysis in \autoref{methods}.

@@

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}). In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs. We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{cc} \hline
parameter & constaint  \\ \hline
x \& y position & $\pm5$ pixels from input value \\
integrated magnitude & 0 -- 40 \\ 
\Reff\ & 0.2 -- 750 pixels \\ 
S\'ersic n & 0.1 -- 8 \\ 
axial ratio & 0 -- 1 \\
position angle & -360 -- 360 \\ \hline

\end{tabular}
\end{center}
\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
\label{constrtable}
\end{table}%

With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit. With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc. The core will be the smaller of the two components fit by \textsc{Galfit}.

\subsubsection{Selection of CCGs}
\label{ccgsel}

\noindent We use the AIMSS sample to select a maximum radius for our CCGs: 800 pc. This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs. RESOLVE's lower stellar mass limit (quote, and include in RESOLVE section above) restricts us from reaching down to UCD masses.

Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B). Figure 1 shows their distribution in stellar mass and \Reff\ compared to other RESOLVE galaxies and the AIMSS CSSs.

\section{Data and Methods}
\label{methods}

\subsection{Photometry: colors, stellar masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo. \citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.

\subsection{Environmental Metrics}
\label{env}
\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments. \citet{Moffett2015}

@@

\noindent As noted in the Introduction, the velocity dispersion of a galaxy is an extremely helpful tool when testing formation scenarios. We describe the data reduction and analysis to derive $\sigma$ for our CCG sample in this section.

\subsubsection{SOAR spectroscopy}
\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile. We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup. From this absorption-line setup, we are able to derive velocity dispersions. We use the supremely-efficient 2100 l/mm VPH grating and cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335. To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.

The

@@

\noindent We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}. This code fits many model spectra (cite Maraston) to the observed input spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Colors and Star formation rates}
\noindent 
* FIGURE: FSMGR vs Mbary/stars for RESOLVE, CCGs, and AIMSS \\
* FIGURE: SFR vs. Mbary/stars for RESOLVE, CCGs, and AIMSS \\

\noindent Figure \#A shows the u-r colors of our CCG sample plotted against M$_{\rm bary}$, compared to the RESOLVE sample as a whole. An unsual finding is that XX CCGs live on the blue sequence, a previsouly rare color for CSSs. REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".

Figure \#B shows FSMGR vs. M$_{\rm bary}$ for the same objects. As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr). This again goes against the common thought that CSSs are ``red and dead".

Here discuss more the envelope vs non-enveloped CCGs and how their popultions may differ.

\subsection{Environments}
\noindent 
 *FIGURE: nearest neighbor and group halo mass\\
* FIGURE: group n vs group halo mass  \\
* Tie in Huxor's cE, idea of ejection from groups, how environment would effect CCGs

\subsection{Kinematics}
\noindent * why kinematics are important for formation scenario discernment\\
* FIGURE: ppxf fits for spectroscopic data to derive velocity dispersions \\
* FIGURE: velocity dispersion vs. stellar mass

>>>>

\documentclass[iop,apj]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\title{Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Mark N. Norris\altaffilmark{3}}
\author{Callie Hood\altaffilmark{1}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{Amanda J. Moffett\altaffilmark{1,4}}
\author{David V. Stark\altaffilmark{1}}
\author{the RESOLVE Team}
\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599,
USA}
\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
\affil{$^4$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
way, Crawley, WA 6009, Australia}
\begin{abstract}
We analyze the complete set of 96 compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments. We perform one and two component S\'ersic fits on the galaxies in the RESOLVE sample using \textsc{Galfit} to produce seeing-deconvolved effective radius (\Reff) measurements. These one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we subsequently perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk. We finalize the CCG sample for those galaxies with core-only (first component) radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. We quantify the amount of light in the core and envelope of each CCG by performing fixed two S\'ersic fits on UKIDSS $Y$-band imaging, and taking the ratio of the fluxes in each component. The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated. With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive the colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars. We find that CCGs naturally occur in a range of environments from isolated to cluster. We compare velocity dispersions of CCGs derived from Gemini IFU data and SOAR spectroscopy to velocity dispersions of other RESOLVE galaxies. We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively. Initial results show several CCGs following the dissipative formation track.
\end{abstract}

\keywords{galaxies: formation, evolution --- surveys}
\maketitle

@@

\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es). Different types of CSSs include ultra compact dwarf galaxies (UCDs; \citet{Phillipps2001}), compact elliptical galaxies (cEs; \citet{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).  There are many unanswered questions about CSSs, typically involving how they form and evolve through time. One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size. Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.

UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \citet{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\citet{Drinkwater2000}, \citet{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\citet{Bekki2001}, \citet{Bekki2003}, \citet{Jennings2015}, \citet{Zhang2015}). \citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546. \citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy, lending more evidence toward tidal stripping being a common for UCDs.

Meanwhile, cEs have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}). They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (\citet{Choi2002}, \citet{Graham2002}), or as a part of the low mass extension to the elliptical galaxy population. The evidence for tidal stripping includes finding tidal streams near cEs (\citet{SmithCastelli2008a}, \citet{Chilingarian2009}) and one cE, studied in \citet{Kormendy1997} that is believed to host a central massive black hole. On the other hand, \citet{Kormendy2012a} argue that cEs are the extension of normal elliptical galaxies.

dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \citet{Norris2014}). Similarly to cEs, dEs and dE,Ns are thought to be either tidally stripped remnants (\citet{Crnojevi2014} find dEs in M31 that show signs of tidal stripping) or the low mass extension to elliptical galaxies \citep{Crawford2016}. They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched. There is some evidence that dE,Ns are the progenitors of UCDs (\citet{Pfeffer2013}, \citet{Zhang2015}, \citet{Liu2015}).

Clues to how a CSS is formed may be given by their environments. UCDs, cEs, dEs have all been found in clusters (for UCDs:\citet{Price2009}, \citet{Madrid2010}, \citet{Hasegan2005}, \citet{Jones2006}, \citet{Mieske2009}, \citet{Wehner2007}, \citet{Misgeld2008}; for cEs: \citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}; and dEs: \citep{SmithCastelli2012}, \citet{Koo1994}, \citet{Guzman1996}, \citet{Crawford2016}). Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups. Lastly, only cEs have been found in isolated environments: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$ Mpc.

Given the similarities in formation scenarios and environments for these CSSs, we propose to study these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff\ sizes. Critical to this study is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments. Previous studies have mainly focused on selecting targets in the group/cluster environments, since this route is often more convenient. Our goal is thus to create a complete and volume-limited sample of compact galaxies across all environments so that we may examine their formation and evolution.

This paper presents the preliminary results of this work, characterizing the colors, star formation histories, environments, and preliminary kinematics of the first complete, volume-limited sample of CCGs. The paper is organized as follows. We explain our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} in \autoref{deconv}. We then explain the selection of the CCG sample from the RESOLVE survey in \autoref{CCGs}. We then describe our photometric and spectroscopic data and analysis in \autoref{methods}. We gives our results in \autoref{results}. Lastly, our results are summarized in \autoref{conclusions}.

@@

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2016}). In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs. We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{cc} \hline
parameter & constaint  \\ \hline
x \& y position & $\pm5$ pixels from input value \\
integrated magnitude & 0 -- 40 \\ 
\Reff\ & 0.2 -- 750 pixels \\ 
S\'ersic n & 0.1 -- 8 \\ 
axial ratio & 0 -- 1 \\
position angle & -360 -- 360 \\ \hline
\end{tabular}
\end{center}
\caption{Summary of the constraints imposed on our \textsc{Galfit} models for our initial one component fits for the entire RESOLVE sample.}
\label{constrtable}
\end{table}%

\noindent We use all of the above to obtain a one component, deconvolved fit for every galaxy in the RESOLVE survey. We then perform the two component fits as follows. We use the output of the one component fit as the basis of the input file for the two component fit. The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed). We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit. This gives \textsc{Galfit} an idea to fit on both a core and envelope. The PSF, image, and mask image will all be the same as before. We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section. In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit. The constraints for each parameter are the same for both sets. We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over constrain our fits.

For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.

\subsubsection{Selection of CCGs}
\label{CCGs}

\begin{figure*}[t]
\begin{center}
\includegraphics{CCGpics.eps}
\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to envelope+core to core-only. Images are taken from the SDSS-DR8 image list tool. The central image is rf0492, a CCG with possible ram pressure stripping origins (see \autoref{kin}).}
\label{fig:pics}
\end{center}
\end{figure*}

\noindent Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies. We use the AIMSS sample to select a maximum cutoff core-only radius for CCGs at 800 pc. This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs. RESOLVE's lower stellar mass limit of  restricts us from reaching down to UCD masses.

We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc. Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored". After this selection, we are left with 124 galaxies in the CCG candidate sample.

Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic fit is constrained to always be larger than that of the first S\'ersic fit, and (3) the S\'ersic n of the second component is held constant at 1 for an exponentially decreasing disk profile. We let the values of \Reff, the integrated magnitude, b/a ratio, and PA change for both fits. By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic fit) and disky envelope (the second S\'ersic fit) for each CCG candidate.

We then examine the fits by eye and create our final CCG sample by selecting where the core \Reff\ $< 800$ pc and $\chi^2/\nu < 1.3$ to again exclude poor fits. Our sample is thus comprised of 96 CCGs in total (63 from RESOLVE-A and 33 from RESOLVE-B). This represents $\sim6$\% of the total RESOLVE galaxy sample. \autoref{fig:radius} shows their distribution in stellar mass and decomposed \Reff\ compared to other RESOLVE galaxies and the AIMSS cEs and dEs. For the RESOLVE sample, we are plotting the one component fits, while for the CCGs, we are plotting the core \Reff\ from the fixed two component fits.

We quantify the amount of light in the core vs. the envelope by taking a ratio of the fluxes of the core and the envelope. The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. For each plot in this paper, we color code the CCGs by the logarithm of the flux ratio. CCGs with more light in the envelope will have log(flux ratio) $<$ 0, and will hereafter be called ``envelope-dominated' CCGs. CCGs with more light in the core will have log(flux ratio) $>$ 0, and will hereafter be called ``core-dominated'' CCGs. CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs. See \autoref{fig:pics} for examples of CCGs on this scale. There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead. Where this happens (5 out of 96 cases), we classify this fit as either all core/envelope depending on which component was bad (log(flux ratio) = -1 or 1). We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component. When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).

We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values. There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.

\begin{figure*}[b]
\begin{center}
\includegraphics{Reff_Mstars.eps}
\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CCSs of the AIMSS catalog. In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff. The CCG sample is using the core \Reff\ of the two component fits, which is why they may appear separated from the full RESOLVE sample. The colors of the CCGs represent the logarithm of the flux ratio between the core and envelope. Galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $\sim \pm 1$ will have more light in the core (+1) or envelope (-1).}
\label{fig:radius}
\end{center}
\end{figure*}

\section{Methods}
\label{methods}

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in \citet{Eckert2015}. The main differences in this processing are (1) improved sky subtraction following Blanton et al. (2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).

Colors, stellar masses and fractional stellar mass growth rates (FSMGR) are then derived from these $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in \citet{Kannappan2007}, \citet{Kannappan2009}, and \citet{Kannappan2013}. FSMGR is similar to a star formation rate, but it instead gives the ratio of stellar mass created in the last Gyr to the stellar mass previously existing. Therefore, an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr.

The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al. in prep.). We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.

\subsection{Environmental Metrics}
\label{env}
\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments. We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy. The group halo mass allows us to look for CCGs that are M32--Andromeda analogs where tidal stripping may be at play, or conversely look for CCGs in large groups where ram-pressure stripping could occur. The distance to neighboring galaxies lets us examine if interaction may occur or look for analogs of the isolated galaxies found by \citet{Huxor2013} and \citet{Paudel2014}.

Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006}, and the masses of these group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}. More information on group identification can be found in \citet{Moffett2015}. The nearest neighbor distances are computed using the RA, Dec, and redshifts of each galaxy and along with spherical geometry principles.

@@

\subsubsection{SOAR spectroscopy}
\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile. We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup. With this absorption-line setup, we are able to derive velocity dispersions. We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335. To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.

The reduction process is as follows: we use standard IRAF tasks to perform bias and overscan subtraction, trimming of the science data to remove unnecessary spatial coverage, and flat fielding. We then use \texttt{LA\_COSMIC} \citep{vanDokkum2001} to clean cosmic rays from each science exposure. We next complete a wavelength calibration and transformation, and then perform object tracing and extraction into a 1D spectrum using the IRAF task apall. We lastly combine the individual exposures using the IRAF task scombine.

@@

\noindent We then derive $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}. This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$. A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skews the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy. Future work will include implementing a stellar rotation subtraction routine for these fits, but preliminary testing by binning the spectra to $1''$ instead of to \Reff\ shows little change between the derived $\sigma$ values.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{rf0078ppxffit.eps}
\caption{Plotted here in black is a summed Gemini-South IFU spectrum for the CCG rf0078. Overplotted in red is the pPXF best fit model spectrum. The spectrum is zoomed-in to show the MgB triplet fit at $\sim 5275$ \AA.}
\label{fig:ppxffit}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{results}
\subsection{Colors and Star formation rates}

\begin{figure*}[t!]
\begin{center}
\includegraphics[scale=0.65]{sfr_mbary.eps}
\caption{\textbf{(a.)} On the left we plot the $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample. \textbf{(b.)} On the right we have plotted the FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample. }
\label{fig:fsmgr}
\end{center}
\end{figure*}
